\subsection{Account Abstract}

\subsubsection{Features}

Eigen NCW is a Modular Multisig Wallet, which is a self-custodial wallet that allows users:
\newline

\textbf{Manage Assets}. Eigen NCW supports multi-signature, that is, wallet transactions require the authorization of multiple private key holders. For example, a 3–3 wallet is a multi-signature wallet that is shared by three people and requires three signatures to sign a transaction. A 2–3 wallet is a multi-signature wallet that is shared by three people and requires two signatures to sign a transaction.
\newline

\textbf{Recover owner by social recovery}. Eigen NCW satisfies the above characteristics well as a social recovery wallet. When the wallet owner forgets the private key, he/she can start social recovery by initiating multi-signature to recover his/her wallet. It's better for users' crypto assets.
\newline

\textbf{Lockable}. Users can lock their wallets if they find something vulnerable, and unlock them whenever they want.
\newline

\textbf{Payment Limitation}. The smart contract wallet supports fine-grained payment management, including large payment limits and daily payment limits, which means if the amount succeeds the limits, multiple signatures mechanism is triggered to execute the transaction, which needs more than half guardians to approve. And these limit parameters can be set by the users.

\subsubsection{Characteristics}

Eigen NCW have some highligh chracteristics:
\newline

\textbf{Upgradeable and Modularized}. Eigen NCW adopts a modular design, a simple base wallet holds the funds and identity of a user. A set of authorized modules can invoke the wallet. Each module handles a specific piece of the Wallet logic and the modules can be added/removed/upgraded. The modular structure means wallet owners can freely upgrade their wallets. Users can upgrade functionality by adding and removing modules to enhance the functionality of their wallets.
\newline

\textbf{Security}. Use multi-signature and social recovery mechanisms to manage users' assets and improve the security of their assets.
\newline

\textbf{Scalability}. The modular design ensures the scalability of the wallet, users can upgrade the functionality by adding and removing modules to enhance the functionality of the wallet.
\newline

\textbf{Simplicity}. Many of the features of Eigen NCW are user-friendly, simple enough, and easy to understand for a large, incremental user base outside of the crypto world. Low mental overhead: as much as possible, our wallet doesn't require users to learn strange new habits or exert mental effort to always remember to follow certain patterns of behavior.
